# Shiny's head

Shiny app has four individual parts: head, two parts of the body and tail. The two parts contributing to the body are _server_ and _interface (UI)_. The head is where the shiny package gets intitated and the tail part is where two parts of the body _server_ and _interface (UI)_ get knitted and the shiny app is deployed. 

## One file
This is a basic Shiny's skeleton in the file format of *app.R*:
```{r eval=FALSE}
library(shiny)                          # Head       - loading the shiny package
ui <- fluidPage()                       # Upper body - setting up the interface
server <- function(input, output) {}    # Lower body - setting up the server side
shinyApp(ui= ui, server = server)       # Tail       - knitting both sides together
```

## Two files
For two separate files format Shiny, the *ui*.R will rewrite as
```{r eval=FALSE}
library(shiny)
shinyUI(fluidPage())
```

and *server.R* rewrite as
```{r eval=FALSE}
library(shiny)
shinyServer(function(input, output) {})
```
